\papertitle

### 2014-03-17 final-report/paper.tex
Intro for arch

\section{Approach}

@@

@@

For example, the data for how many workers are working on a certain fragment as described in Section~\ref{sec:fragments} is generated from the even log using a query to select only events for the root operators (the operators that have no parent in the same fragment) in each fragment and a custom map function that carries state. The state is an integer that is incremented when the operator is called on a worker and decremented when the operator returns.

>>>>

\section{Approach}
\label{sec:approach}

@@

The task of the back-end is to log when operators are called, when the call returns and when data is sent to another worker. Using this data and simple transformations, we can obtain the information necessary to create the visualizations to answer the questions in Section~\ref{sec:approach}.

@@

For example, the data for how many workers are working on a certain fragment as described in Section~\ref{sec:fragments} is generated from the event log using a query to select only events for the root operators (the operators that have no parent in the same fragment) in each fragment and a custom map function that carries state. The state is an integer that is incremented when the operator is called on a worker and decremented when the operator returns.
